Lab News

### 2023-07-13 news.qmd
init

---
title: ""
pagetitle: "CarterLab | Home"
toc: false
---

![](images/uni-hall-front.jpg)

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions. We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios. We also conduct metascience research to gain important insights into research practices within kinesiology and sport science. We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/) within the [Faculty of Science](https://www.science.mcmaster.ca/) at [McMaster University](https://www.mcmaster.ca/).

#### Recent lab news ---------

@@

>>>>

---
title: "Lab News"
pagetitle: "CarterLab | News"
toc: false
---

@@

<font color="#d08770">[May 19 2023].</font> **New preprint**. St. Germain, L., McKay, B., Tandon, C., Seedu, J., Barbera, L., Carrillo, C., Brown, D.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *SportR*$\chi$*iv*. doi: <https://doi.org/10.51224/SRXIV.298>

<font color="#d08770">[April 13 2023].</font> **Paper accepted**. McKay, B., Bacelar, M.F.B., Parma, J.O., Miller, M.W., & Carter, M.J. The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*.
